Large-scale spatiotemporal variation in vital rates and population dynamics of an alpine bird

### 2024-09-16 Manuscript_Nater_etal.qmd
Updated code reference

![Simplified graphical representation of the "targets pipeline" for the multi-area modelling setup. Upward facing triangles are functions, downward facing triangles are general options/arguments, circles are objects and outputs (="targets") created as part of the workflow. For the full representation, download the repository and call "targets::tar_visnetwork()". The manual R and Nix/GNUparallel implementations of the workflow have the same structure and built on the same functions and relationships. ](Figures/Workflow_layout.png){#fig-workflow width="424"}

@@

All code, including the three pipelines, can be found in the project's repository on GitHub: <https://github.com/ErlendNilsen/OpenPop_Integrated_DistSamp>. The results presented in this paper were created using version 2.1 of the code [@chloernater_2024_10572340].

>>>>

![Simplified graphical representation of the "targets pipeline" for the multi-area modelling setup. Upward facing triangles are functions, downward facing triangles are general options/arguments, circles are objects and outputs (="targets") created as part of the workflow. For the full representation, download the repository and call "targets::tar_visnetwork()". The manual R and Nix/GNUparallel implementations of the workflow have the same structure and built on the same functions and relationships.](Figures/Workflow_layout.png){#fig-workflow width="424"}

@@

All code, including the three pipelines, can be found in the project's repository on GitHub: <https://github.com/ErlendNilsen/OpenPop_Integrated_DistSamp>. The results presented in this paper were created using version 2.1 of the code [@rypeIDSM2024].
